\begin{acknowledgements}
I like to convey my sincerest gratitude to my advisor Dr. Sandhu. I have  learned so many things from him. Every moment I was accompanied by him, I have learned, learned a lot. Besides all his expertises that have guided me toward developing this thesis, his wisdom and generosity have also guided me to become a better human being. I can remember how naive and unprofessional I was when I joined his team. Dr. Sandhu took lot of patience, love and care to develop the insight within me that have guided me and will guide me through out my life. 

I also like to thank Dr. Ram for his generosity and guidance. He has always helped me to develop  new ideas, be critical on own works. He has inspired me every time I meet him.

I also like to thank <committees>... for their valuable comments, time and insight in organizing this thesis.

I also owe to Farhan Patwa, who is always encouraging and inspiring. Besides his leadership skills, he has guided me a lot in learning and contributing to OpenStack. 

Finally, I would like to acknowledge Computer Science faculties, Suzan Tanaka from ICS, Susan Alen from the CS department,  my friends (especially Ziaul Haque Olive) and colleagues at UTSA. You were always helpful. You have guided me towards the self I am today.

\begin{singlespace}
\emph{This Masters Thesis/Recital Document or Doctoral Dissertation
was produced in accordance with guidelines which permit the inclusion
as part of the Masters Thesis/Recital Document or Doctoral Dissertation
the text of an original paper, or papers, submitted for publication.
The Masters Thesis/Recital Document or Doctoral Dissertation must
still conform to all other requirements explained in the Guide for
the Preparation of a Masters Thesis/Recital Document or Doctoral Dissertation
at The University of Texas at San Antonio. It must include a comprehensive
abstract, a full introduction and literature review, and a final overall
conclusion. Additional material (procedural and design data as well
as descriptions of equipment) must be provided in sufficient detail
to allow a clear and precise judgment to be made of the importance
and originality of the research reported. }

\emph{It is acceptable for this Masters Thesis/Recital Document or
Doctoral Dissertation to include as chapters authentic copies of papers
already published, provided these meet type size, margin, and legibility
requirements. In such cases, connecting texts, which provide logical
bridges between different manuscripts, are mandatory. Where the student
is not the sole author of a manuscript, the student is required to
make an explicit statement in the introductory material to that manuscript
describing the students contribution to the work and acknowledging
the contribution of the other author(s). The signatures of the Supervising
Committee which precede all other material in the Masters Thesis/Recital
Document or Doctoral Dissertation attest to the accuracy of this statement.}\end{singlespace}
\end{acknowledgements}