%\section{Equivalence of LaBAC and \newline 2-sorted-RBAC}
\label{sec:equivalence}
\twoSortedRBAC{} \cite{two-sorted-rbac} is an interesting extension of Role Based Access Control which breaks the duality of roles (users and permissions perspectives) into proper roles ($\properRole$) as group of users and demarcation ($\demarcation$) as group of permissions. User inheritance is maintained with proper role hierarchy ($\properRoleHierarchy$) and permission inheritance is maintained with demarcation hierarchy ($\demarcationHierarchy$). The connection between proper roles and demarcation is maintained by the grant relation ($G$) which enumerates (proper role, demarcation) pairs. For example, for proper roles and demarcations given in Figure \ref{fig:two-sorted-rbac-example}, G includes following tuples - \{(manager, red), (employee, amber)\}. Note that \twoSortedRBAC{} \cite{two-sorted-rbac} also includes negative roles and demarcations which we do not consider here.



\twoSortedRBAC{} is compelling in many ways. It introduces a higher administrative level (through grant relation) for access management. User-role assignment ($UR^+ \subseteq U \times \properRole$) and demarcation-permission assignment ($PD^+ \subseteq P \times \demarcation$), along with administration of grant relation can be carried out more independently and distributively. Moreover, the authors shows that, \twoSortedRBAC{} enables many-to-many administrative mutations which leads to organizational scalability.  In many-to-many mutation, by granting a (proper role, demarcation) pair, all users in the proper role get all  permissions in the demarcation which, as the authors shows cannot be achieved by standard RBAC \cite{nist-rbac}.


 \input{ABAC16/demarcation-example-diagram.tex}
 

The benefits of \twoSortedRBAC{} can also be realized through LaBAC. For example, user to $\uLabel{}$ value assignments, object to \oLabel{} value assignments and authorization policies are analogous to $\properRoleHierarchy$, $\demarcationHierarchy$ and grant relation in \twoSortedRBAC{} and  can also be carried out independently. On the other hand, many-to-many administrative mutation can also be achieved. For example, the LaBAC policy, $\Policy_{op1}\equiv \{(manager, (red,op1))\}$ in Figure \ref{fig:two-sorted-rbac-to-labac-example},  enables every   $manager$ to perform operation $op1$ on every object labeled with  $(red,op1)$. 

\input{ABAC16/two-sorted-rbac-to-labac-example-diagram.tex}

 \input{ABAC16/demarcation-in-labac.tex}
 
 In fact, LaBAC is similar to \twoSortedRBAC{} in spirit. While \twoSortedRBAC{} is more role oriented, LaBAC is attribute oriented. In the following of this section, we show equivalence of LaBAC and \twoSortedRBAC{} with respect to their theoretical  expressive power. In order to establish the equivalence, we show that any instance of \twoSortedRBAC{} can be expressed in LaBAC and vice-versa.

 
 
Figure  \ref{fig:two-sorted-rbac-to-labac-example} is an example showing configuration of a \twoSortedRBAC{} instance (given in Figure \ref{fig:two-sorted-rbac-example}) in LaBAC. In Figure  \ref{fig:two-sorted-rbac-to-labac-example}, user-label values and its hierarchy directly corresponds to roles and role hierarchy in Figure \ref{fig:two-sorted-rbac-example}. On the other hand, object-label values correspond to Cartesian product of $\demarcation$ and $OPS$.   An object-label value $(d_i, op)$ dominates another object-label value $(d_j, op)$, if demarcation $d_i$ dominates demarcation $d_j$. For example, for demarcations \{$red$, $amber$\} and operations $\{op1,op2\}$ (of Figure \ref{fig:two-sorted-rbac-example}), four object-label values have been defined where $(red,op1)$ dominates $(amber,op1)$ because $red$ dominates $amber$.  For an object-label value $(d,op)$, we assign $(d,op)$ to the object $o$ to if $(o,op)$ is a permission in demarcation $d$. For example, object $o1$ is assigned the value $(red,op1)$ because $(o1,op1)$ is  a permission in demarcation $red$.  On the other hand, user-label values assigned to a user corresponds to his assigned proper roles. Finally, having assigned object-label and user-label values, for each grant relation $(r,d) \in G$,  we specify authorization policy $Policy_{op} \equiv \{(r,(d,op))\}$ so that object labeled with $(d,op)$ are accessed by users with role $r$ for operation $op$. For example, for the grant relation $(manager,red)$ in Figure \ref{fig:two-sorted-rbac-example}, we create a policy $Policy_{op1} \equiv \{(manager, (red,op1))\}$. We do not create  policy $Policy_{op2} \equiv \{(manager, (red,op2))\}$ because there is no permission defined with operation $op2$ in demarcation $red$. Table \ref{tab:two-sorted-rbac-in-labac-table} formally  shows this configuration.
 

 
 % \input{two-sorted-labac-example-diagram.tex}
 
 \input{ABAC16/labac-in-two-sorted-rbac.tex}
 
 
 
 Configuration of \hlabac{} in \twoSortedRBAC{} is given in Table \ref{tab:labac-in-two-sorted-rbac-table}. Segment I represents elements of LaBAC model and Segment II shows the configuration.  In the configuration, user-label values and its hierarchy are used as proper roles and proper role hierarchy. Object-label values are used as names for demarcations. For an object-label value $ol\in OL$, let $O_{ol}$ be the objects labeled with $ol$. For each policy $policy_{op} \equiv \{(ul, ol)\}$ in LaBAC, we create a grant relation $(ul,ol)$ in \twoSortedRBAC{}. Further, assign permission (o,op) in demarcation named $ol$ for $o \in O_{op}$. Note that \twoSortedRBAC{} does not distinguish between users and sessions as we do in LaBAC. For this reason, we omit LaBAC sessions while showing equivalence with \twoSortedRBAC{}.
 
 
 

  
  Here we use \hlabac{} to configure \twoSortedRBAC{} for convenience. In fact,  \clabac{} is the minimalistic model that is equivalent to \twoSortedRBAC{}. In Figure \ref{fig:expressiveness-spectrum}, we show summary of expressive power of different LaBAC models. The dashed box represents the minimalistic LaBAC model required to configure other models and solid box represents the LaBAC model that we use for our convenience. 

%We acknowledge the more formal  approach of \textit{state matching reduction} or simply \textit{reduction} \cite{tripli} for establishing equivalence between access control models. For simplicity and absence of state transition functions (administrative models) for some models discussed here, we adopt a simplified and conventional approach for the establishment of  equivalence.

The construction of Tables \ref{tab:two-sorted-rbac-in-labac-table} and \ref{tab:labac-in-two-sorted-rbac-table} and other constructions given in the rest of this paper can be cast in the formal approach of \cite{tripli}. So, these models are equivalent in the sense of state-matching reduction. 

  \input{ABAC16/expressiveness-spectrum.tex}
 
