
\documentclass{sig-alternate-2013}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\usepackage{natbib}
\usepackage{url}
\usepackage[toc,page]{appendix}
\MakeOuterQuote{"}
\newfont{\mycrnotice}{ptmr8t at 7pt}
\newfont{\myconfname}{ptmri8t at 7pt}
\let\crnotice\mycrnotice%
\let\confname\myconfname%

\permission{Permission to make digital or hard copies of part or all of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage, and that copies bear this notice and the full citation on the first page. Copyrights for third-party components of this work must be honored. For all other uses, contact the owner/author(s). Copyright is held by the author/owner(s).}
\conferenceinfo{CODASPY'15,}{March 2--4, 2015, San Antonio, Texas, USA.} 
\copyrightetc{ACM \the\acmcopyr}
\crdata{978-1-4503-3191-3/15/03. \\
http://dx.doi.org/10.1145/2699026.2699124}
\clubpenalty=10000 
\widowpenalty = 10000

\begin{document}




\title{ Content Level Access Control for OpenStack Swift Storage }


\numberofauthors{5}
\author{
\alignauthor Prosunjit Biswas\\
	\affaddr{Univ. of Texas at San Antonio}\\
	\affaddr{San Antonio, TX, USA}\\
	\email{prosun.csedu@gmail.com}
%\alignauthor Yun Zhang\\
%	\affaddr{Univ. of Texas at San Antonio}\\
%	\affaddr{San Antonio, TX, USA}\\
%	\email{amy.u.zhang@gmail.com}
\alignauthor Farhan Patwa\\
	\affaddr{Univ. of Texas at San Antonio}\\
	\affaddr{San Antonio, TX, USA}\\
	\email{farhan.patwa@utsa.edu }
%\and
\alignauthor Ravi Sandhu\\
	\affaddr{Univ. of Texas at San Antonio}\\
	\affaddr{San Antonio, TX, USA}\\
	\email{ravi.sandhu@utsa.edu}	
%\alignauthor Paul Rad\\
%	\affaddr{Univ. of Texas at San Antonio}\\
%	\affaddr{San Antonio, TX, USA}\\
%	\email{paul.rad@rackspace.com}
	}

\date{15 Sept. 2014}

\maketitle

\input{abstract.tex}
\input{introduction.tex}
\input{background.tex}

\input{implementation.tex}
\input{performance.tex}

\input{conclusion.tex}


\bibliographystyle{plain}
\bibliography{references}


\end{document}
